The Evolution of Phenotypically Invariant Genetic Networks

### 2018-08-16 review-responses.tex

\begin{point}{p 11.}
    Approximating the optimal set $\mathcal{N}$ by a quadratic surface should only be accurate if
we look at the genetic divergence at small time scales. This should be at least mentioned.
\end{point}

\reply{
}

\begin{point}{end of p11.}
    $1/( \frac{d}{du} D(x + uz))$ should be evaluated at $u = 0$.
\end{point}

\reply{
}

\begin{point}{p12. Third paragraph}
    $\sqrt{4 \omega T/N_e} \sim \gamma/\sigma_N$.
    I guess the underlying assumption here is that
    $\sigma_S \ll \sqrt{4 \omega \sigma^2_N T/N_e}$?
\end{point}

\reply{
}

\begin{point}{p12. before eq. 7.}
    $\mu = c_\mu \gamma T /N_e$. Why is $\mu$ proportional to $\gamma$?
\end{point}

\reply{
}

\begin{point}{Fig 7.}
    I have one important issue with this figure (and the assumptions of the underly-
ing quantitative genetic model). If one wants to be consistent with the assumption that
parental populations drift along the evolutionary ridge, I think one would need to assume
that selection is strong enough to constraint the mean of the population on the surface. This
would presumably require that $\sigma S /\gamma \ll 1$. First, I think this assumption (or something
alternative to that) should be made explicit in the text. Secondly, it seems to me that this
assumption is not satisfied for panel A and C: under the range of parameters proposed by
the authors, the parental populations could easily drift away from the optimal set, and in
particular, the heuristics derived in the main text would not be satisfied.
\end{point}

\reply{
}

\begin{point}{}
    Finally, it would be worth mentioning several old and recent works relating genetic drift
to speciation : Yamagushi and Iwasa, several articles by Gavrilets et al. (I think several
citations are missing here), and Mirò Pina and Schertzer.
\end{point}

\reply{
}
